---
title: "Sentiment Analysis May 8 2020"
author: "Rob Wells"
date: "5/8/2020"
output: html_document
---

# Sentiment Analysis of Economic Filter corpus of articles, 5,306 articles from 2000-2019

Code is adapted from EF_Sentiment-local.R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "")
getwd()
```

Load libraries
```{r include=FALSE}
#install.packages("sentimentr")
#install.packages("tidytext")
#install.packages("textdata")
#install.packages("rio")
library(textdata)
library(sentimentr)
library(tidytext)
library(rio)
library(tidyverse)
```

Load dictionaries

```{r}
afinn <-get_sentiments("afinn")
bing <- get_sentiments("bing")
```

```{r}
#Have to load NRC separately
#http://sentiment.nrc.ca/lexicons-for-research/
# nrc <- rio::import("/Users/robwells/Dropbox/Current_Projects/China Notes  Background/NRC-Sentiment-Emotion-Lexicons/NRC-Emotion-Lexicon-v0.92/Older Versions/NRC-Emotion-Lexicon-v0.92-InManyLanguages.xlsx")
# nrc <- janitor::clean_names(nrc)
# nrc <- nrc %>% 
#   select(english_word, positive, negative, anger, anticipation, disgust, fear, joy, sadness, surprise, trust)
# colnames(nrc)[1] <- "word"
# write.csv(nrc, "nrc.csv")
# 
# nrc %>% 
#   count(positive, negative)
# 
# nrc1 <- rio::import("/Users/robwells/Dropbox/Current_Projects/China Notes  Background/NRC-Sentiment-Emotion-Lexicons/NRC-Emotion-Lexicon-v0.92/NRC-Emotion-Lexicon-Wordlevel-v0.92.txt")
# colnames(nrc1)[1:3] <- c("word", "sentiment", "score")
# write.csv(nrc1, "nrc1.csv")
# #
```

```{r}
setwd("~/Dropbox/Current_Projects/ChinaFDI")
nrc1 <- rio::import("nrc1.csv")

nrc2 <- nrc1 %>% 
  filter(score >=1)
```

# Load Economic Filter data

```{r}
setwd("~/Dropbox/Current_Projects/ChinaFDI")
YearWords <- rio::import("./EconomicFilter/YearWords.csv")
```
# Filter noise like President, Trump,  Premier

```{r}
junk <- c("trump", "president", "china", "chinese", "american", "trumps", "canada", "european", "chinas", 
          "beijing", "north", "south", "korea", "mexico", "washington", "mstar", "united", "states", "government",
          "administration", "white", "house", "xi", "premier", "lighthizer", "wto")
```

```{r}
YearWords <- YearWords %>% 
  filter(!word  %in% junk)
```

### Preferred method of calculating sentiment: Sentiment * Word Frequency
```{r}
total_BINGYearsentiment <- YearWords  %>%
  inner_join(bing, by = "word") %>% 
   select(year, word, sentiment, n) 
head(total_BINGYearsentiment)
```


```{r}
sum(total_BINGYearsentiment$n)
```

```{r}
x <- total_BINGYearsentiment
```

### Transforming the 'negative' and 'positive' into a numeric value
```{r}
x$score  <- x$sentiment

x$score <- gsub("positive", "1", x$score)
x$score <- gsub("negative", "-1", x$score)
x$score <- as.numeric(x$score)
glimpse(x)
```


```{r}
x<- x %>% 
  mutate(newscore = (score*n))
head(x)
```         

```{r}
bing_by_year_EF <- x %>%
   group_by(year, sentiment) %>% 
     summarise(yrtotal = sum(newscore))
```

-- Total Score

```{r}
average_bing_by_year_EF <- x %>%
   group_by(year, sentiment, newscore) %>% 
     summarise(yrtotal = sum(newscore)) %>% 
    summarise(yr_average = mean(newscore))  
head(average_bing_by_year_EF)
```

-- Average Postive / Negative Score

```{r}
bing_AVG_EF_sent_year <- x %>% 
   group_by(year, sentiment) %>% 
  summarise(yr_average = mean(newscore))  
head(bing_AVG_EF_sent_year)
```



```{r}
#write.csv(bing_by_year_EF, "EF_bing_year_total.csv")
#write.csv(bing_AVG_EF_sent_year, "bing_AVG_EF_sent_year.csv")


```

### Combined average sentiment score
```{r}
xx <- x %>%
   group_by(year) %>% 
     summarise(EF_yravg = mean(newscore))
#write.csv(xx, "/Users/robwells/Dropbox/Current_Projects/ChinaFDI/Sentiment Analysis/EF_single_bing_year.csv")
head(xx)
```

```{r}
mean(xx$EF_yravg)
```

```{r}
xx %>% 
ggplot(aes(x= year, y= EF_yravg, color = EF_yravg > -2.134966, size = 4)) +
  geom_point() +
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(legend.position = "none") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(title = "China News Sentiment by Year", 
       subtitle = "Bing Average Sentiment, Economic News",
       caption = "Blue= Above average sentiment of -2.1. Red = Below average sentiment. \n Source: ProQuest - Economic Filter Search. 5,306 articles
       Graphic by Rob Wells. 5-14-2020",
       x=" ",
       y="Sentiment: Negative -> Positive") 

#ggsave("AvgChina_Sentiment.png",device = "png",width=10,height=8, dpi=800)

```

# Custom Sentiment Analysis

-- This script comes from Custom Sentiment list 7-5-19.R, and a May 25 script.

bing <- get_sentiments("bing")
#bing columns are word and sentiment
afinn <- get_sentiments("afinn")
#afinn columns are word and score

### Importing custom list of 176 trade terms curated by Wells and Zeng. 
--  Full list is in Box, Negative-Postiive Key Terms on Trade 4-18-19.xlsx
-- trade_terms columns are word and score
```{r}
trade_terms <- rio::import("./Sentiment Analysis/trade_sentiment_5-25.csv")
head(trade_terms)
```

```{r}
head(YearWords)
```
## Total Custom Sentiment for EF

### Preferred method of calculating sentiment: Sentiment * Word Frequency
```{r}
total_CustomYearsentiment <- YearWords  %>%
  inner_join(trade_terms, by = "word") %>% 
   select(year, word, rating, n) 
head(total_CustomYearsentiment)
```


```{r}
sum(total_CustomYearsentiment$n)
```

```{r}
a <- total_CustomYearsentiment
```


```{r}
a<- a %>% 
  mutate(newscore = (rating*n))
head(a)
```         



### Table of custom sentiment score by year for Economic Filter
## Insert average here

### Average custom sentiment score
```{r}
custom_by_year_EF <- a %>%
   group_by(year) %>% 
     summarise(EFyravg = mean(newscore))
head(custom_by_year_EF)
write.csv(custom_by_year_EF, "./Sentiment Analysis/custom_by_year_EF.csv")
```


```{r}
#Average custom sentiment score is -7.804261
mean(custom_by_year_EF$EFyravg)
```

```{r}
custom_by_year_EF %>% 
ggplot(aes(x= year, y= EFyravg, color = EFyravg > -7.804261, size = 4)) +
  geom_point() +
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(legend.position = "none") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(title = "Custom Sentiment: China Economic News", 
       subtitle = "Custom Sentiment Score, Chinese Investment in U.S.",
       caption = "Blue= Above average sentiment of -7.8. Red = Below average sentiment. \n Source: ProQuest - Economic Filter Search. 5,306 articles
       Graphic by Rob Wells. 5-17-2020",
       x=" ",
       y="Sentiment: Negative -> Positive") 

ggsave("CustomAvgChina_Sentiment.png",device = "png",width=10,height=8, dpi=800)

```

### Notes below
### Notes below  
### Notes below
### Notes below


## Notes Below - Older Version of Totaled Scores, Not Averaged

```{r}
#Older version that summed the custom sentiment.
#Newer version does the average
custom_by_year_TOTAL_EF <- a %>%
   group_by(year) %>% 
     summarise(custom_total = sum(newscore))
head(custom_by_year_TOTAL_EF)
#write.csv(custom_by_year_TOTAL_EF, "./Sentiment Analysis/custom_by_year_TOTAL_EF.csv")
```

-- Validation test by year. All OK
```{r}
#test by year
wtf <- a %>% 
  filter(year =="2019") %>% 
  group_by(year)
```

```{r}
sum(wtf$newscore)
```
All OK


-- Average custom sentiment score is -1072.5
```{r}
mean(custom_by_year_EF$custom_total)
```


## Older version of summing the number of terms for sentiment total

# Create totalled sentiment by year: Bing

Total Bing Sentiment. This version only counts sentiment and not word frequency. It is replaced by an improved method at line 119 that tabulates sentiment and word frequency
```{r}
z <- YearWords  %>%
  inner_join(bing, by = "word") %>%
  group_by(year) %>% 
    count(sentiment) %>% 
    arrange(desc(n)) %>% 
    spread(sentiment, n, fill=0) %>% 
    mutate(article_score = positive - negative)
head(z)
```    

### This section is the count of articles divided into the sentiment score for a normalized metric of sentiment / article

#averages the scores of articles with the companies mentioned
xyz <- cos_sum_sentiment %>% 
  select(pattern, pub.x, article_score, date) %>% 
  group_by(pattern) %>% 
  summarise(avg = mean(article_score)) %>% 
  arrange(desc(avg))

#Count of articles by company
count <- cos_sum_sentiment %>% 
  select(pattern, article_nmbr) %>% 
  group_by(pattern) %>% 
  count(pattern) %>% 
  ungroup()

#join the sentiment and article totals
both <- xyz %>% 
  inner_join(count)
#
#Ratio of average score to number of articles
both$ratio <- both$avg/both$n
#
#Add total score
both <- both %>% 
  inner_join(abc)

company_totals <- both %>% 
  select(pattern, avg, n, ratio, total)

write_csv(company_totals, "company_totals-7-27-19.csv")

