---
title: "Sentiment Index 5-14-2020"
author: "Wells"
date: "5/14/2020"
output: html_document
---
# Charts of Bing and Custom Sentiment Indexes of China General and Economic News

The following material walks through the construction of a single sentiment index for general and economic news using the Bing sentiment library.   

    Details on Bing lexicon: Dictionary of 6,786 words
    https://juliasilge.github.io/tidytext/reference/sentiments.html
    https://www.cs.uic.edu/~liub/FBS/sentiment-analysis.html   

Then the general and economic news is assessed using a custom library of 177 terms specifically focused on trade discourse whose sentiment were scored by the authors.   

    https://github.com/profrobwells/ChinaFDI/blob/master/Sentiment%20Analysis/trade_sentiment_5-25.csv


```{r}
#Optional to clear out the environment
rm(list=ls())
```

Load libraries
```{r include=FALSE}

library(tidyverse)
library(tidytext)
library(XML)
library(janitor)
library(kableExtra)
library(lubridate)
library(ggpubr)
```


# Join and compare Bing sentiment scores for Economic and Broad Filter

```{r}
#import EF sentiment score
#data originates from Sentiment Econ Filter 5-8-2020.rmd and Sentiment Broad Filter 5-14-2020.rmd

EFsent <- rio::import("./Sentiment Analysis/EF_single_bing_year_6_22_2020.csv")
BFsent <- rio::import("./Sentiment Analysis/BF_single_bing_year_6_22_2020.csv")

BF_EFsent <- EFsent %>% 
  inner_join(BFsent, by = "year") 

BF_EFsent <- BF_EFsent %>% 
  select(year, EF_yravg, BF_yravg)
head(BF_EFsent)
```

The following chart shows how sentiment in broader news soured dramatically in 2017, as Trump entered office and began the trade war. The economic news didn't show the dramatic decline in sentiment. 

```{r}
ggplot(data= BF_EFsent) +
geom_line(mapping = aes(x= year, y= BF_yravg, color = "Red", size = 2)) +
geom_line(mapping = aes(x= year, y= EF_yravg, color = "Blue", size = 2)) +
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(legend.position = "none") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(title = "Economic, General China News Sentiment by Year", 
       subtitle = "Average Sentiment, News on Chinese Investment in U.S.",
       caption = "Red= Broad Filter General News. Blue = Economic News. \n Source: ProQuest - Broad Search. 5,209 articles; Economic, 5,306 articles
       Graphic by Rob Wells. 6-22-2020",
       x=" ",
       y="Sentiment: Negative -> Positive") 

ggsave("./Sentiment Analysis/BF_EF_Sentiment.png",device = "png",width=10,height=8, dpi=800)

```


# Correlation of EF and BF Sent by Year
### A Pearson's correlation test also shows the weakness in comparing the two sentiments.

### This test shows p-value = 0.04128, which suggests a somewhat significant relationship between average negative sentiment in the Broad Filter and Economic Filterc news articles

```{r}
cor.test(BF_EFsent$EF_yravg, BF_EFsent$BF_yravg, method = "pearson")
```


```{r}
ggscatter(BF_EFsent, x = "EF_yravg", y = "BF_yravg", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Economic Filter News Sentiment", ylab = "Broad Filter News Sentiment")

```

```{r}
  glimpse(BF_EFsent)
```


# Combined single sentiment score called index

```{r}
#Adding the Bing sentiment scores
BF_EFsent <- BF_EFsent %>% 
  mutate(index = (EF_yravg + BF_yravg))
head(BF_EFsent)
#write.csv(BF_EFsent, "./Sentiment Analysis/news_sentiment_index.csv")
```


The average sentiment is -2.254839
```{r}
mean(BF_EFsent$index)
```

### A chart of China News Sentiment by Year. This is the sum of the Economic and General News Sentiment

```{r}
BF_EFsent %>% 
ggplot(aes(x= year, y= index, color = "red", size = 3)) +
#ggplot(aes(x= year, y= index, color = index > -4.469829, size = 3)) +
  geom_line() +
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(legend.position = "none") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(title = "China News Sentiment by Year", 
       subtitle = "Index Economic and General News Sentiment on Chinese Investment in U.S.",
       caption = "Source: ProQuest - BroadFilter - Economic Filter Searches. Graphic by Rob Wells. 6-22-2020",
       x=" ",
       y="Sentiment: Negative -> Positive") 

ggsave("./Sentiment Analysis/sentiment_index3.png",device = "png",width=10,height=8, dpi=800)

```

### The calculation below is the average of the Economic and General News scores into a new index. This average helps smooth out the variations in the data.

```{r}
#Averaging the Bing sentiment scores
z <- BF_EFsent %>% 
  mutate(index = (EF_yravg + BF_yravg)/2)
head(z)
#write.csv(BF_EFsent, "./Sentiment Analysis/news_sentiment_index.csv")
```

The average sentiment is -1.127419
```{r}
mean(z$index)
```


### This chart of the average sentiment index shows the same pattern but on a scale without as much dramatic variation.

```{r}
z %>% 
ggplot(aes(x= year, y= index, color = "red", size = 3)) +
#ggplot(aes(x= year, y= index, color = index > -2.234914, size = 3)) +
  geom_line() +
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(legend.position = "none") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(title = "China News Sentiment by Year", 
       subtitle = "Index Average Economic and General News Sentiment on Chinese Investment in U.S.",
       caption = "Source: ProQuest - BroadFilter - Economic Filter Searches. Graphic by Rob Wells. 6-22-2020",
       x=" ",
       y="Sentiment: Negative -> Positive") 

ggsave("./Sentiment Analysis/sentiment_index3.png",device = "png",width=10,height=8, dpi=800)

```


# Custom Sentiment Score

### Join and compare custom sentiment scores for Economic and Broad Filter

### The Custom Sentiment Score is based on a custom dictionary of 177 terms specifically focused on trade discourse whose sentiment were scored by the authors

### Here is the Economic News scored by the Custom Sentiment Score

```{r}
#import EF custom sentiment score from Sentiment Broad Filter 5-14-2020
EFcust <- rio::import("./Sentiment Analysis/custom_by_year_EF.csv")
colnames(EFcust)[3] <- c("EF_custom_total")
head(EFcust)
```

### Here is the General News scored by the Custom Sentiment Score

```{r}
BFcust <- rio::import("./Sentiment Analysis/custom_by_year_BF.csv")
colnames(BFcust)[3] <- c("BF_custom_total")
head(BFcust)
```

### General and Economic news scores joined by year

```{r}
BF_EFcust <- EFcust %>% 
  inner_join(BFcust, by = "year") 

```

### Custom Scores for Economic and General Table Cleaned

```{r}
BF_EFcust  <- BF_EFcust  %>% 
  select(year, EF_custom_total, BF_custom_total)
head(BF_EFcust)
```

### A new index is created with the average of the general and economic custom scores

```{r}

BF_EFcust <- BF_EFcust %>% 
  mutate(index = (EF_custom_total + BF_custom_total)/2)
head(BF_EFcust)
write.csv(BF_EFcust, "./Sentiment Analysis/BF_EFcust.csv")
```

# The average sentiment for this new custom index is -9.072425

```{r}

mean(BF_EFcust$index)
```

# A chart of the new custom sentiment index for both general and economic news

```{r}
BF_EFcust %>% 
ggplot(aes(x= year, y= index, color = "red", size = 3)) +
#ggplot(aes(x= year, y= index, color = index > -4.469829, size = 3)) +
  geom_line() +
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(legend.position = "none") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(title = "Custom Sentiment, China News", 
       subtitle = "Sentiment Economic, General News: Chinese Investment in U.S.",
       caption = "Source: ProQuest - BroadFilter - Economic Filter Searches. Graphic by Rob Wells. 6-22-2020",
       x=" ",
       y="Sentiment: Negative -> Positive") 

#ggsave("./Sentiment Analysis/BF_EFcust.png",device = "png",width=10,height=8, dpi=800)

```
### And for comparison sake, here is a repeat of the sentiment using the Bing index

### We see the custom index shows a sharper decline after 2015 but also a slight uptick at the end. Yet this scale of sentiment is far more negative that the Bing values below.

```{r echo=FALSE}
z %>% 
ggplot(aes(x= year, y= index, color = "red", size = 3)) +
#ggplot(aes(x= year, y= index, color = index > -2.234914, size = 3)) +
  geom_line() +
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(legend.position = "none") +
   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   labs(title = "China News Sentiment by Year", 
       subtitle = "Index Average Economic and General News Sentiment on Chinese Investment in U.S.",
       caption = "Source: ProQuest - BroadFilter - Economic Filter Searches. Graphic by Rob Wells. 5-14-2020",
       x=" ",
       y="Sentiment: Negative -> Positive") 


```

```{r}
#---------------------------------------------------------------------------
# Sentiments
#---------------------------------------------------------------------------
#Import
EF <- rio::import("./EconomicFilter/Economicfilter2020.csv")

#Tokenize the TEXT table)


reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"
TEXT_token <- EF %>%
  filter(!str_detect(Text, '^"')) %>%
  #mutate(text = str_replace_all(text, "https://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
  unnest_tokens(word, Text, token = "regex", pattern = reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))

#Clean out ' character in word columm of TEXT_token
#example: 'growing
TEXT_token$word <- 
  gsub("'","", TEXT_token$word)

#remove spaces
TEXT_token$word <- 
  gsub(" ","", TEXT_token$word)


#TEXT_token <- select (TEXT_token, c(headline, article_nmbr, linenumber, word2))
#colnames(TEXT_token)[4] <- "word"

#save
#write.csv(TEXT_token, "./EconomicFilter/EF_tokenized.csv")


#install.packages("sentimentr")
#install.packages("tidytext")
#install.packages("textdata")
library(textdata)
library(sentimentr)
library(tidytext)

bing <- get_sentiments("bing")

#------------------------
#Have to load NRC separately
#http://sentiment.nrc.ca/lexicons-for-research/
# nrc <- rio::import("/Users/robwells/Dropbox/Current_Projects/China Notes  Background/NRC-Sentiment-Emotion-Lexicons/NRC-Emotion-Lexicon-v0.92/Older Versions/NRC-Emotion-Lexicon-v0.92-InManyLanguages.xlsx")
# nrc <- janitor::clean_names(nrc)
# nrc <- nrc %>% 
#   select(english_word, positive, negative, anger, anticipation, disgust, fear, joy, sadness, surprise, trust)
# colnames(nrc)[1] <- "word"
# write.csv(nrc, "nrc.csv")
# 
# nrc %>% 
#   count(positive, negative)
# 
# nrc1 <- rio::import("/Users/robwells/Dropbox/Current_Projects/China Notes  Background/NRC-Sentiment-Emotion-Lexicons/NRC-Emotion-Lexicon-v0.92/NRC-Emotion-Lexicon-Wordlevel-v0.92.txt")
# colnames(nrc1)[1:3] <- c("word", "sentiment", "score")
# write.csv(nrc1, "nrc1.csv")
# #
nrc1 <- rio::import("nrc1.csv")


nrc2 <- nrc1 %>% 
  filter(score >=1)

EF_sentiment <- EF_type %>%
  inner_join(bing, by = "word")
```  


-- **Transforming the 'negative' and 'positive' into a numeric value**
```{r}
#x$score  <- x$sentiment
EF_sentiment$score <- EF_sentiment$sentiment

EF_sentiment$score <- gsub("positive", "1", EF_sentiment$score)
EF_sentiment$score <- gsub("negative", "-1", EF_sentiment$score)
EF_sentiment$score <- as.numeric(EF_sentiment$score)
glimpse(EF_sentiment)
```

```{r}
library(lubridate)
EF_sentiment$Date <- ymd(EF_sentiment$Date)
#Create year field
EF_sentiment$year <- year(EF_sentiment$Date)
```

```{r}
EF_sentiment %>%
  group_by(year, Pub) %>% 
  #summarize(mean = mean(score))  %>% 
  ggplot(aes(x = year, y = score)) +
  geom_col(show.legend = FALSE) +
  geom_smooth(se=FALSE)+
  scale_x_continuous(breaks=c(2000:2019)) +
  theme(axis.text.x = element_text(angle=90)) +
  #scale_x_date() +
  #scale_y_reverse() +
  #coord_flip()  +
  labs(title = "Sentiment News Articles- China Economic News", 
       subtitle = "Sentiment Score: NYT, WSJ, LAT, WP, IUT: Economic Filter, 2000-2019.",
       caption = "Bing sentiment dictionary, 4,046 articles. Source: ProQuest. Graphic by Rob Wells",
       x="Year",
       y="Sentiment score")
#Created Sentiment News-Only Years 7-3
```